---
title: "Followers to Founders — Extended Demographic Interaction Models"
author: "Vincent V. Crowns"
format: html
editor: visual
---

# Overview

This file contains **9 exploratory PLM random effects models** — 3 per outcome, each testing a different moderator set against the conjoint attributes.

-   **Model A** — Conjoint × Demographics (age_range, gender, income_level)
-   **Model B** — Conjoint × Social Media Platforms
-   **Model C** — Conjoint × Known Influencers

All models include conjoint × conjoint interactions from the main analysis file as a baseline. Estimated coefficient counts are all well under the n = 208 respondent ceiling. Compare RMSE across models to determine which moderator set explains the most variance per outcome.

------------------------------------------------------------------------

```{r}
### Setup
library(plm)
library(tidyverse)
library(car)
data <- read_csv("FtF_cleaned.csv")
```

------------------------------------------------------------------------

## Straightlining Check

```{r}
straightliners <- data |>
  group_by(ResponseId) |>
  summarise(
    sd_purchase = sd(purchase_intent,       na.rm = TRUE),
    sd_honesty  = sd(percived_honesty,      na.rm = TRUE),
    sd_auth     = sd(percived_authenticity, na.rm = TRUE)
  ) |>
  filter(sd_purchase == 0 | sd_honesty == 0 | sd_auth == 0) |>
  pull(ResponseId)

cat("Straightliners removed:", length(straightliners), "\n")
cat("Respondents remaining:", n_distinct(data$ResponseId) - length(straightliners), "\n")

data <- data |> filter(!ResponseId %in% straightliners)
```

------------------------------------------------------------------------

## Cleaning & Dummy-Coding

```{r}
cleaned_data <- data |>

  mutate(
    plt_instagram = as.integer(str_detect(platforms, "Instagram")),
    plt_snapchat  = as.integer(str_detect(platforms, "Snapchat")),
    plt_tiktok    = as.integer(str_detect(platforms, "TikTok")),
    plt_x         = as.integer(str_detect(platforms, "X \\(Twitter\\)")),
    plt_youtube   = as.integer(str_detect(platforms, "YouTube")),
    plt_twitch    = as.integer(str_detect(platforms, "Twitch")),
    plt_facebook  = as.integer(str_detect(platforms, "FaceBook"))
  ) |>

  mutate(
    inf_shaq    = as.integer(str_detect(influencers_known, "Shaquille O'Neal")),
    inf_kylie   = as.integer(str_detect(influencers_known, "Kylie Jenner")),
    inf_mrbeast = as.integer(str_detect(influencers_known, "MrBeast")),
    inf_logan   = as.integer(str_detect(influencers_known, "Logan Paul")),
    inf_curry   = as.integer(str_detect(influencers_known, "Stephen Curry")),
    inf_taylor  = as.integer(str_detect(influencers_known, "Taylor Swift")),
    inf_ryan    = as.integer(str_detect(influencers_known, "Ryan Reynolds")),
    inf_ksi     = as.integer(str_detect(influencers_known, "KSI")),
    inf_charli  = as.integer(str_detect(influencers_known, "Charli D'Amelio"))
  ) |>

  dplyr::select(-platforms, -influencers_known) |>

  group_by(influencer, number_of_comments, number_of_likes, writting_style) |>
  mutate(scenario = cur_group_id()) |>
  ungroup() |>
  drop_na() |>
  group_by(ResponseId) |>
  filter(n() > 1) |>
  ungroup()

colSums(is.na(cleaned_data))
glimpse(cleaned_data)
```

```{r}
### Convert conjoint attributes to factors
cleaned_data <- cleaned_data |>
  mutate(
    number_of_comments = as.factor(number_of_comments),
    number_of_likes    = as.factor(number_of_likes),
    writting_style     = as.factor(writting_style),
    influencer         = as.factor(influencer)
  )

cleaned_data$influencer <- relevel(cleaned_data$influencer, ref = "0")
```

```{r}
### Build panel data frame
cleaned_data$task <- ave(cleaned_data$scenario, cleaned_data$ResponseId, FUN = seq_along)
pdata <- pdata.frame(cleaned_data, index = c("ResponseId", "task"))
```

## PLM Random Effects Models

### Purchase Intent

*"I would consider purchasing this product."*

```{r}
# Base model
model_purchase <- plm(
  purchase_intent ~
    number_of_comments + number_of_likes + writting_style + influencer +
    influencer_interaction + social_media_use + product_purchase +
    plt_instagram + plt_snapchat + plt_tiktok + plt_x +
    plt_youtube + plt_twitch + plt_facebook +
    inf_shaq + inf_kylie + inf_mrbeast + inf_logan + inf_curry +
    inf_taylor + inf_ryan + inf_ksi + inf_charli,
  data  = pdata,
  model = "random"
)
summary(model_purchase)
```

### Perceived Honesty

*"This influencer seems honest."*

```{r}
# Base model
model_honesty <- plm(
  percived_honesty ~
    number_of_comments + number_of_likes + writting_style + influencer +
    influencer_interaction + social_media_use + product_purchase +
    plt_instagram + plt_snapchat + plt_tiktok + plt_x +
    plt_youtube + plt_twitch + plt_facebook +
    inf_shaq + inf_kylie + inf_mrbeast + inf_logan + inf_curry +
    inf_taylor + inf_ryan + inf_ksi + inf_charli,
  data  = pdata,
  model = "random"
)
summary(model_honesty)
```

## Perceived Authenticity

*"This influencer seems authentic."*

```{r}
# Base model
model_auth <- plm(
  percived_authenticity ~
    number_of_comments + number_of_likes + writting_style + influencer +
    influencer_interaction + social_media_use + product_purchase +
    plt_instagram + plt_snapchat + plt_tiktok + plt_x +
    plt_youtube + plt_twitch + plt_facebook +
    inf_shaq + inf_kylie + inf_mrbeast + inf_logan + inf_curry +
    inf_taylor + inf_ryan + inf_ksi + inf_charli,
  data  = pdata,
  model = "random"
)
summary(model_auth)
```

------------------------------------------------------------------------

# Purchase Intent Models

*"I would consider purchasing this product."*

------------------------------------------------------------------------

## Model A — Conjoint × Demographics

*Moderators: age_range, gender, income_level (\~148 coefficients)*

```{r}
model_purchase_A <- plm(
  purchase_intent ~

    number_of_comments + number_of_likes + writting_style + influencer +

    age_range + gender + income_level + education + employment_status +
    marritial_status + race + influencer_interaction + social_media_use +
    product_purchase + plt_instagram + plt_snapchat + plt_tiktok + plt_x +
    plt_youtube + plt_twitch + plt_facebook + inf_shaq + inf_kylie +
    inf_mrbeast + inf_logan + inf_curry + inf_taylor + inf_ryan +
    inf_ksi + inf_charli +

    number_of_comments:number_of_likes +
    number_of_comments:writting_style +
    number_of_comments:influencer +
    number_of_likes:writting_style +
    number_of_likes:influencer +
    writting_style:influencer +

    number_of_comments:age_range +
    number_of_likes:age_range +
    writting_style:age_range +
    influencer:age_range +

    number_of_comments:gender +
    number_of_likes:gender +
    writting_style:gender +
    influencer:gender +

    number_of_comments:income_level +
    number_of_likes:income_level +
    writting_style:income_level +
    influencer:income_level,

  data  = pdata,
  model = "random"
)
summary(model_purchase_A)

## Report Findings Here:
##
##
```

------------------------------------------------------------------------

## Model B — Conjoint × Platforms

*Moderators: all 7 platform dummies (\~113 coefficients)*

```{r}
model_purchase_B <- plm(
  purchase_intent ~

    number_of_comments + number_of_likes + writting_style + influencer +

    age_range + gender + income_level + education + employment_status +
    marritial_status + race + influencer_interaction + social_media_use +
    product_purchase + plt_instagram + plt_snapchat + plt_tiktok + plt_x +
    plt_youtube + plt_twitch + plt_facebook + inf_shaq + inf_kylie +
    inf_mrbeast + inf_logan + inf_curry + inf_taylor + inf_ryan +
    inf_ksi + inf_charli +

    number_of_comments:number_of_likes +
    number_of_comments:writting_style +
    number_of_comments:influencer +
    number_of_likes:writting_style +
    number_of_likes:influencer +
    writting_style:influencer +

    number_of_comments:plt_instagram + number_of_comments:plt_snapchat +
    number_of_comments:plt_tiktok + number_of_comments:plt_x +
    number_of_comments:plt_youtube + number_of_comments:plt_twitch +
    number_of_comments:plt_facebook +
    number_of_likes:plt_instagram + number_of_likes:plt_snapchat +
    number_of_likes:plt_tiktok + number_of_likes:plt_x +
    number_of_likes:plt_youtube + number_of_likes:plt_twitch +
    number_of_likes:plt_facebook +
    writting_style:plt_instagram + writting_style:plt_snapchat +
    writting_style:plt_tiktok + writting_style:plt_x +
    writting_style:plt_youtube + writting_style:plt_twitch +
    writting_style:plt_facebook +
    influencer:plt_instagram + influencer:plt_snapchat +
    influencer:plt_tiktok + influencer:plt_x +
    influencer:plt_youtube + influencer:plt_twitch +
    influencer:plt_facebook,

  data  = pdata,
  model = "random"
)
summary(model_purchase_B)

## Report Findings Here:
##
##
```

------------------------------------------------------------------------

## Model C — Conjoint × Known Influencers

*Moderators: all 9 known influencer dummies (\~123 coefficients)*

```{r}
model_purchase_C <- plm(
  purchase_intent ~

    number_of_comments + number_of_likes + writting_style + influencer +

    age_range + gender + income_level + education + employment_status +
    marritial_status + race + influencer_interaction + social_media_use +
    product_purchase + plt_instagram + plt_snapchat + plt_tiktok + plt_x +
    plt_youtube + plt_twitch + plt_facebook + inf_shaq + inf_kylie +
    inf_mrbeast + inf_logan + inf_curry + inf_taylor + inf_ryan +
    inf_ksi + inf_charli +

    number_of_comments:number_of_likes +
    number_of_comments:writting_style +
    number_of_comments:influencer +
    number_of_likes:writting_style +
    number_of_likes:influencer +
    writting_style:influencer +

    number_of_comments:inf_shaq + number_of_comments:inf_kylie +
    number_of_comments:inf_mrbeast + number_of_comments:inf_logan +
    number_of_comments:inf_curry + number_of_comments:inf_taylor +
    number_of_comments:inf_ryan + number_of_comments:inf_ksi +
    number_of_comments:inf_charli +
    number_of_likes:inf_shaq + number_of_likes:inf_kylie +
    number_of_likes:inf_mrbeast + number_of_likes:inf_logan +
    number_of_likes:inf_curry + number_of_likes:inf_taylor +
    number_of_likes:inf_ryan + number_of_likes:inf_ksi +
    number_of_likes:inf_charli +
    writting_style:inf_shaq + writting_style:inf_kylie +
    writting_style:inf_mrbeast + writting_style:inf_logan +
    writting_style:inf_curry + writting_style:inf_taylor +
    writting_style:inf_ryan + writting_style:inf_ksi +
    writting_style:inf_charli +
    influencer:inf_shaq + influencer:inf_kylie +
    influencer:inf_mrbeast + influencer:inf_logan +
    influencer:inf_curry + influencer:inf_taylor +
    influencer:inf_ryan + influencer:inf_ksi +
    influencer:inf_charli,

  data  = pdata,
  model = "random"
)
summary(model_purchase_C)

## Report Findings Here:
##
##
```

------------------------------------------------------------------------

# Perceived Honesty Models

*"This influencer seems honest."*

------------------------------------------------------------------------

## Model A — Conjoint × Demographics

```{r}
model_honesty_A <- plm(
  percived_honesty ~

    number_of_comments + number_of_likes + writting_style + influencer +

    age_range + gender + income_level + education + employment_status +
    marritial_status + race + influencer_interaction + social_media_use +
    product_purchase + plt_instagram + plt_snapchat + plt_tiktok + plt_x +
    plt_youtube + plt_twitch + plt_facebook + inf_shaq + inf_kylie +
    inf_mrbeast + inf_logan + inf_curry + inf_taylor + inf_ryan +
    inf_ksi + inf_charli +

    number_of_comments:number_of_likes +
    number_of_comments:writting_style +
    number_of_comments:influencer +
    number_of_likes:writting_style +
    number_of_likes:influencer +
    writting_style:influencer +

    number_of_comments:age_range +
    number_of_likes:age_range +
    writting_style:age_range +
    influencer:age_range +

    number_of_comments:gender +
    number_of_likes:gender +
    writting_style:gender +
    influencer:gender +

    number_of_comments:income_level +
    number_of_likes:income_level +
    writting_style:income_level +
    influencer:income_level,

  data  = pdata,
  model = "random"
)
summary(model_honesty_A)

## Report Findings Here:
##
##
```

------------------------------------------------------------------------

## Model B — Conjoint × Platforms

```{r}
model_honesty_B <- plm(
  percived_honesty ~

    number_of_comments + number_of_likes + writting_style + influencer +

    age_range + gender + income_level + education + employment_status +
    marritial_status + race + influencer_interaction + social_media_use +
    product_purchase + plt_instagram + plt_snapchat + plt_tiktok + plt_x +
    plt_youtube + plt_twitch + plt_facebook + inf_shaq + inf_kylie +
    inf_mrbeast + inf_logan + inf_curry + inf_taylor + inf_ryan +
    inf_ksi + inf_charli +

    number_of_comments:number_of_likes +
    number_of_comments:writting_style +
    number_of_comments:influencer +
    number_of_likes:writting_style +
    number_of_likes:influencer +
    writting_style:influencer +

    number_of_comments:plt_instagram + number_of_comments:plt_snapchat +
    number_of_comments:plt_tiktok + number_of_comments:plt_x +
    number_of_comments:plt_youtube + number_of_comments:plt_twitch +
    number_of_comments:plt_facebook +
    number_of_likes:plt_instagram + number_of_likes:plt_snapchat +
    number_of_likes:plt_tiktok + number_of_likes:plt_x +
    number_of_likes:plt_youtube + number_of_likes:plt_twitch +
    number_of_likes:plt_facebook +
    writting_style:plt_instagram + writting_style:plt_snapchat +
    writting_style:plt_tiktok + writting_style:plt_x +
    writting_style:plt_youtube + writting_style:plt_twitch +
    writting_style:plt_facebook +
    influencer:plt_instagram + influencer:plt_snapchat +
    influencer:plt_tiktok + influencer:plt_x +
    influencer:plt_youtube + influencer:plt_twitch +
    influencer:plt_facebook,

  data  = pdata,
  model = "random"
)
summary(model_honesty_B)

## Report Findings Here:
##
##
```

------------------------------------------------------------------------

## Model C — Conjoint × Known Influencers

```{r}
model_honesty_C <- plm(
  percived_honesty ~

    number_of_comments + number_of_likes + writting_style + influencer +

    age_range + gender + income_level + education + employment_status +
    marritial_status + race + influencer_interaction + social_media_use +
    product_purchase + plt_instagram + plt_snapchat + plt_tiktok + plt_x +
    plt_youtube + plt_twitch + plt_facebook + inf_shaq + inf_kylie +
    inf_mrbeast + inf_logan + inf_curry + inf_taylor + inf_ryan +
    inf_ksi + inf_charli +

    number_of_comments:number_of_likes +
    number_of_comments:writting_style +
    number_of_comments:influencer +
    number_of_likes:writting_style +
    number_of_likes:influencer +
    writting_style:influencer +

    number_of_comments:inf_shaq + number_of_comments:inf_kylie +
    number_of_comments:inf_mrbeast + number_of_comments:inf_logan +
    number_of_comments:inf_curry + number_of_comments:inf_taylor +
    number_of_comments:inf_ryan + number_of_comments:inf_ksi +
    number_of_comments:inf_charli +
    number_of_likes:inf_shaq + number_of_likes:inf_kylie +
    number_of_likes:inf_mrbeast + number_of_likes:inf_logan +
    number_of_likes:inf_curry + number_of_likes:inf_taylor +
    number_of_likes:inf_ryan + number_of_likes:inf_ksi +
    number_of_likes:inf_charli +
    writting_style:inf_shaq + writting_style:inf_kylie +
    writting_style:inf_mrbeast + writting_style:inf_logan +
    writting_style:inf_curry + writting_style:inf_taylor +
    writting_style:inf_ryan + writting_style:inf_ksi +
    writting_style:inf_charli +
    influencer:inf_shaq + influencer:inf_kylie +
    influencer:inf_mrbeast + influencer:inf_logan +
    influencer:inf_curry + influencer:inf_taylor +
    influencer:inf_ryan + influencer:inf_ksi +
    influencer:inf_charli,

  data  = pdata,
  model = "random"
)
summary(model_honesty_C)

## Report Findings Here:
##
##
```

------------------------------------------------------------------------

# Perceived Authenticity Models

*"This influencer seems authentic."*

------------------------------------------------------------------------

## Model A — Conjoint × Demographics

```{r}
model_auth_A <- plm(
  percived_authenticity ~

    number_of_comments + number_of_likes + writting_style + influencer +

    age_range + gender + income_level + education + employment_status +
    marritial_status + race + influencer_interaction + social_media_use +
    product_purchase + plt_instagram + plt_snapchat + plt_tiktok + plt_x +
    plt_youtube + plt_twitch + plt_facebook + inf_shaq + inf_kylie +
    inf_mrbeast + inf_logan + inf_curry + inf_taylor + inf_ryan +
    inf_ksi + inf_charli +

    number_of_comments:number_of_likes +
    number_of_comments:writting_style +
    number_of_comments:influencer +
    number_of_likes:writting_style +
    number_of_likes:influencer +
    writting_style:influencer +

    number_of_comments:age_range +
    number_of_likes:age_range +
    writting_style:age_range +
    influencer:age_range +

    number_of_comments:gender +
    number_of_likes:gender +
    writting_style:gender +
    influencer:gender +

    number_of_comments:income_level +
    number_of_likes:income_level +
    writting_style:income_level +
    influencer:income_level,

  data  = pdata,
  model = "random"
)
summary(model_auth_A)

## Report Findings Here:
##
##
```

------------------------------------------------------------------------

## Model B — Conjoint × Platforms

```{r}
model_auth_B <- plm(
  percived_authenticity ~

    number_of_comments + number_of_likes + writting_style + influencer +

    age_range + gender + income_level + education + employment_status +
    marritial_status + race + influencer_interaction + social_media_use +
    product_purchase + plt_instagram + plt_snapchat + plt_tiktok + plt_x +
    plt_youtube + plt_twitch + plt_facebook + inf_shaq + inf_kylie +
    inf_mrbeast + inf_logan + inf_curry + inf_taylor + inf_ryan +
    inf_ksi + inf_charli +

    number_of_comments:number_of_likes +
    number_of_comments:writting_style +
    number_of_comments:influencer +
    number_of_likes:writting_style +
    number_of_likes:influencer +
    writting_style:influencer +

    number_of_comments:plt_instagram + number_of_comments:plt_snapchat +
    number_of_comments:plt_tiktok + number_of_comments:plt_x +
    number_of_comments:plt_youtube + number_of_comments:plt_twitch +
    number_of_comments:plt_facebook +
    number_of_likes:plt_instagram + number_of_likes:plt_snapchat +
    number_of_likes:plt_tiktok + number_of_likes:plt_x +
    number_of_likes:plt_youtube + number_of_likes:plt_twitch +
    number_of_likes:plt_facebook +
    writting_style:plt_instagram + writting_style:plt_snapchat +
    writting_style:plt_tiktok + writting_style:plt_x +
    writting_style:plt_youtube + writting_style:plt_twitch +
    writting_style:plt_facebook +
    influencer:plt_instagram + influencer:plt_snapchat +
    influencer:plt_tiktok + influencer:plt_x +
    influencer:plt_youtube + influencer:plt_twitch +
    influencer:plt_facebook,

  data  = pdata,
  model = "random"
)
summary(model_auth_B)

## Report Findings Here:
##
##
```

------------------------------------------------------------------------

## Model C — Conjoint × Known Influencers

```{r}
model_auth_C <- plm(
  percived_authenticity ~

    number_of_comments + number_of_likes + writting_style + influencer +

    age_range + gender + income_level + education + employment_status +
    marritial_status + race + influencer_interaction + social_media_use +
    product_purchase + plt_instagram + plt_snapchat + plt_tiktok + plt_x +
    plt_youtube + plt_twitch + plt_facebook + inf_shaq + inf_kylie +
    inf_mrbeast + inf_logan + inf_curry + inf_taylor + inf_ryan +
    inf_ksi + inf_charli +

    number_of_comments:number_of_likes +
    number_of_comments:writting_style +
    number_of_comments:influencer +
    number_of_likes:writting_style +
    number_of_likes:influencer +
    writting_style:influencer +

    number_of_comments:inf_shaq + number_of_comments:inf_kylie +
    number_of_comments:inf_mrbeast + number_of_comments:inf_logan +
    number_of_comments:inf_curry + number_of_comments:inf_taylor +
    number_of_comments:inf_ryan + number_of_comments:inf_ksi +
    number_of_comments:inf_charli +
    number_of_likes:inf_shaq + number_of_likes:inf_kylie +
    number_of_likes:inf_mrbeast + number_of_likes:inf_logan +
    number_of_likes:inf_curry + number_of_likes:inf_taylor +
    number_of_likes:inf_ryan + number_of_likes:inf_ksi +
    number_of_likes:inf_charli +
    writting_style:inf_shaq + writting_style:inf_kylie +
    writting_style:inf_mrbeast + writting_style:inf_logan +
    writting_style:inf_curry + writting_style:inf_taylor +
    writting_style:inf_ryan + writting_style:inf_ksi +
    writting_style:inf_charli +
    influencer:inf_shaq + influencer:inf_kylie +
    influencer:inf_mrbeast + influencer:inf_logan +
    influencer:inf_curry + influencer:inf_taylor +
    influencer:inf_ryan + influencer:inf_ksi +
    influencer:inf_charli,

  data  = pdata,
  model = "random"
)
summary(model_auth_C)

## Report Findings Here:
##
##
```

------------------------------------------------------------------------

# RMSE Comparison

Run after both this file and FtF_Analysis_bay.qmd have been executed in the same R session.

```{r}
plm_rmse <- function(mod) sqrt(mean(residuals(mod)^2))

rmse_all <- tibble(
  outcome = rep(c("purchase_intent", "percived_honesty", "percived_authenticity"), each = 4),
  model   = rep(c("Original Interaction", "Model A: Demographics",
                  "Model B: Platforms",   "Model C: Known Influencers"), times = 3),
  rmse    = c(
    plm_rmse(model_purchase), plm_rmse(model_purchase_A),
    plm_rmse(model_purchase_B),   plm_rmse(model_purchase_C),
    plm_rmse(model_honesty),  plm_rmse(model_honesty_A),
    plm_rmse(model_honesty_B),    plm_rmse(model_honesty_C),
    plm_rmse(model_auth),     plm_rmse(model_auth_A),
    plm_rmse(model_auth_B),       plm_rmse(model_auth_C)
  )
) |> arrange(outcome, rmse)

print(rmse_all, n = Inf)
```
