---
title: "Followers to Founders"
author: "Vincent V. Crowns"
format: html
editor: visual
---

```{r}
### Setup the data and libraries
library(plm)
library(tidyverse)
library(tidymodels)
library(car)
library(brms)
data <- read_csv("FtF_cleaned.csv")
```

------------------------------------------------------------------------

## Straightlining Check

Remove any respondent who gave the same answer across all 3 scenarios for at least one outcome variable (purchase_intent, percived_honesty, or percived_authenticity).

```{r}
# Identify straightliners — constant response on ANY outcome across their scenarios
straightliners <- data |>
  group_by(ResponseId) |>
  summarise(
    sd_purchase  = sd(purchase_intent,       na.rm = TRUE),
    sd_honesty   = sd(percived_honesty,      na.rm = TRUE),
    sd_auth      = sd(percived_authenticity, na.rm = TRUE)
  ) |>
  filter(sd_purchase == 0 | sd_honesty == 0 | sd_auth == 0) |>
  pull(ResponseId)

cat("Straightliners removed:", length(straightliners), "\n")
cat("Respondents remaining:", n_distinct(data$ResponseId) - length(straightliners), "\n")

data <- data |> filter(!ResponseId %in% straightliners)
```

------------------------------------------------------------------------

## Cleaning & Dummy-Coding

```{r}
cleaned_data <- data |>

  # --- Dummy-code platforms ---
  mutate(
    plt_instagram = as.integer(str_detect(platforms, "Instagram")),
    plt_snapchat  = as.integer(str_detect(platforms, "Snapchat")),
    plt_tiktok    = as.integer(str_detect(platforms, "TikTok")),
    plt_x         = as.integer(str_detect(platforms, "X \\(Twitter\\)")),
    plt_youtube   = as.integer(str_detect(platforms, "YouTube")),
    plt_twitch    = as.integer(str_detect(platforms, "Twitch")),
    plt_facebook  = as.integer(str_detect(platforms, "FaceBook"))
  ) |>

  # --- Dummy-code influencers_known ---
  mutate(
    inf_shaq    = as.integer(str_detect(influencers_known, "Shaquille O'Neal")),
    inf_kylie   = as.integer(str_detect(influencers_known, "Kylie Jenner")),
    inf_mrbeast = as.integer(str_detect(influencers_known, "MrBeast")),
    inf_logan   = as.integer(str_detect(influencers_known, "Logan Paul")),
    inf_curry   = as.integer(str_detect(influencers_known, "Stephen Curry")),
    inf_taylor  = as.integer(str_detect(influencers_known, "Taylor Swift")),
    inf_ryan    = as.integer(str_detect(influencers_known, "Ryan Reynolds")),
    inf_ksi     = as.integer(str_detect(influencers_known, "KSI")),
    inf_charli  = as.integer(str_detect(influencers_known, "Charli D'Amelio"))
  ) |>

  # --- Drop original multi-value columns ---
  dplyr::select(-platforms, -influencers_known) |>

  # --- Scenario ID and cleaning ---
  group_by(influencer, number_of_comments, number_of_likes, writting_style) |>
  mutate(scenario = cur_group_id()) |>
  ungroup() |>
  drop_na() |>
  group_by(ResponseId) |>
  filter(n() > 1) |>
  ungroup()

colSums(is.na(cleaned_data))
glimpse(cleaned_data)
```

```{r}
### Convert binary conjoint attributes to factors
# number_of_comments, number_of_likes, writting_style are 0/1 binary
# influencer has 3 levels (-1, 0, 1) — effects-coded; 0 set as reference
cleaned_data <- cleaned_data |>
  mutate(
    number_of_comments = as.factor(number_of_comments),
    number_of_likes    = as.factor(number_of_likes),
    writting_style     = as.factor(writting_style),
    influencer         = as.factor(influencer)
  )

# Set 0 (mid-tier influencer) as the reference level for influencer
cleaned_data$influencer <- relevel(cleaned_data$influencer, ref = "0")
```

```{r}
### Build panel data frame
cleaned_data$task <- ave(cleaned_data$scenario, cleaned_data$ResponseId, FUN = seq_along)
pdata <- pdata.frame(cleaned_data, index = c("ResponseId", "task"))
```

------------------------------------------------------------------------

## Preprocessing & Cross-Validation

```{r}
# Work from cleaned_data (non-panel tibble) for tidymodels
set.seed(42)

# 10-fold CV split — stratify on ResponseId so each fold has a mix of respondents
cv_folds <- vfold_cv(cleaned_data, v = 10, strata = NULL)

# --- Recipes: one per outcome (update_role cannot promote a var to outcome after the fact) ---
pred_vars <- c("number_of_comments", "number_of_likes", "writting_style", "influencer",
               "age_range", "gender", "income_level", "education", "race",
               "employment_status", "marritial_status",
               "influencer_interaction", "social_media_use", "product_purchase",
               "plt_instagram", "plt_snapchat", "plt_tiktok", "plt_x",
               "plt_youtube", "plt_twitch", "plt_facebook",
               "inf_shaq", "inf_kylie", "inf_mrbeast", "inf_logan", "inf_curry",
               "inf_taylor", "inf_ryan", "inf_ksi", "inf_charli")

make_recipe <- function(outcome, data) {
  f <- as.formula(paste(outcome, "~", paste(pred_vars, collapse = " + ")))
  recipe(f, data = data) |>
    step_novel(all_nominal_predictors()) |>
    step_dummy(all_nominal_predictors()) |>
    step_zv(all_predictors()) |>
    step_normalize(all_numeric_predictors())
}

recipe_purchase <- make_recipe("purchase_intent",       cleaned_data)
recipe_honesty  <- make_recipe("percived_honesty",      cleaned_data)
recipe_auth     <- make_recipe("percived_authenticity", cleaned_data)

# --- Linear regression spec for CV ---
lm_spec <- linear_reg() |> set_engine("lm")

# --- Workflows ---
wf_purchase <- workflow() |> add_recipe(recipe_purchase) |> add_model(lm_spec)
wf_honesty  <- workflow() |> add_recipe(recipe_honesty)  |> add_model(lm_spec)
wf_auth     <- workflow() |> add_recipe(recipe_auth)     |> add_model(lm_spec)

# --- Run 10-fold CV for each outcome ---
cv_purchase <- fit_resamples(wf_purchase, resamples = cv_folds,
                             metrics = metric_set(rmse, rsq, mae))
cv_honesty  <- fit_resamples(wf_honesty,  resamples = cv_folds,
                             metrics = metric_set(rmse, rsq, mae))
cv_auth     <- fit_resamples(wf_auth,     resamples = cv_folds,
                             metrics = metric_set(rmse, rsq, mae))

# --- Summarise CV results ---
cat("=== Purchase Intent CV ===\n");   print(collect_metrics(cv_purchase))
cat("=== Perceived Honesty CV ===\n"); print(collect_metrics(cv_honesty))
cat("=== Perceived Authenticity CV ===\n"); print(collect_metrics(cv_auth))
```

------------------------------------------------------------------------

## PLM Random Effects Models

### Purchase Intent

*"I would consider purchasing this product."*

```{r}
# Base model
model_purchase <- plm(
  purchase_intent ~
    number_of_comments + number_of_likes + writting_style + influencer +
    influencer_interaction + social_media_use + product_purchase +
    plt_instagram + plt_snapchat + plt_tiktok + plt_x +
    plt_youtube + plt_twitch + plt_facebook +
    inf_shaq + inf_kylie + inf_mrbeast + inf_logan + inf_curry +
    inf_taylor + inf_ryan + inf_ksi + inf_charli,
  data  = pdata,
  model = "random"
)
summary(model_purchase)
```

```{r}
# Interaction model
model_purchase_int <- plm(
  purchase_intent ~
    number_of_comments + number_of_likes + writting_style + influencer +
    age_range + gender + income_level + education + race +
    employment_status + marritial_status +
    influencer_interaction + social_media_use + product_purchase +
    plt_instagram + plt_snapchat + plt_tiktok + plt_x +
    plt_youtube + plt_twitch + plt_facebook +
    inf_shaq + inf_kylie + inf_mrbeast + inf_logan + inf_curry +
    inf_taylor + inf_ryan + inf_ksi + inf_charli +
    number_of_comments:number_of_likes +
    number_of_comments:writting_style +
    number_of_comments:influencer +
    number_of_likes:writting_style +
    number_of_likes:influencer +
    writting_style:influencer,
  data  = pdata,
  model = "random"
)
summary(model_purchase_int)

## Report Findings Here:
##
##
```

------------------------------------------------------------------------

### Perceived Honesty

*"This influencer seems honest."*

```{r}
# Base model
model_honesty <- plm(
  percived_honesty ~
    number_of_comments + number_of_likes + writting_style + influencer +
    influencer_interaction + social_media_use + product_purchase +
    plt_instagram + plt_snapchat + plt_tiktok + plt_x +
    plt_youtube + plt_twitch + plt_facebook +
    inf_shaq + inf_kylie + inf_mrbeast + inf_logan + inf_curry +
    inf_taylor + inf_ryan + inf_ksi + inf_charli,
  data  = pdata,
  model = "random"
)
summary(model_honesty)
```

```{r}
# Interaction model
model_honesty_int <- plm(
  percived_honesty ~
    number_of_comments + number_of_likes + writting_style + influencer +
    age_range + gender + income_level + education + race +
    employment_status + marritial_status +
    influencer_interaction + social_media_use + product_purchase +
    plt_instagram + plt_snapchat + plt_tiktok + plt_x +
    plt_youtube + plt_twitch + plt_facebook +
    inf_shaq + inf_kylie + inf_mrbeast + inf_logan + inf_curry +
    inf_taylor + inf_ryan + inf_ksi + inf_charli +
    number_of_comments:number_of_likes +
    number_of_comments:writting_style +
    number_of_comments:influencer +
    number_of_likes:writting_style +
    number_of_likes:influencer +
    writting_style:influencer +
    number_of_comments:plt_instagram + number_of_comments:plt_tiktok +
    number_of_comments:plt_youtube + number_of_comments:plt_x +
    number_of_likes:plt_instagram + number_of_likes:plt_tiktok +
    number_of_likes:plt_youtube + number_of_likes:plt_x +
    writting_style:plt_instagram + writting_style:plt_tiktok +
    writting_style:plt_youtube + writting_style:plt_x +
    influencer:plt_instagram + influencer:plt_tiktok +
    influencer:plt_youtube + influencer:plt_x +
    number_of_comments:inf_kylie + number_of_comments:inf_mrbeast +
    number_of_comments:inf_logan + number_of_comments:inf_taylor +
    number_of_likes:inf_kylie + number_of_likes:inf_mrbeast +
    number_of_likes:inf_logan + number_of_likes:inf_taylor +
    writting_style:inf_kylie + writting_style:inf_mrbeast +
    writting_style:inf_logan + writting_style:inf_taylor +
    influencer:inf_kylie + influencer:inf_mrbeast +
    influencer:inf_logan + influencer:inf_taylor,
  data  = pdata,
  model = "random"
)
summary(model_honesty_int)

## Report Findings Here:
##
##
```

------------------------------------------------------------------------

### Perceived Authenticity

*"This influencer seems authentic."*

```{r}
# Base model
model_auth <- plm(
  percived_authenticity ~
    number_of_comments + number_of_likes + writting_style + influencer +
    influencer_interaction + social_media_use + product_purchase +
    plt_instagram + plt_snapchat + plt_tiktok + plt_x +
    plt_youtube + plt_twitch + plt_facebook +
    inf_shaq + inf_kylie + inf_mrbeast + inf_logan + inf_curry +
    inf_taylor + inf_ryan + inf_ksi + inf_charli,
  data  = pdata,
  model = "random"
)
summary(model_auth)
```

```{r}
# Interaction model
model_auth_int <- plm(
  percived_authenticity ~
    number_of_comments + number_of_likes + writting_style + influencer +
    age_range + gender + income_level + education + race +
    employment_status + marritial_status +
    influencer_interaction + social_media_use + product_purchase +
    plt_instagram + plt_snapchat + plt_tiktok + plt_x +
    plt_youtube + plt_twitch + plt_facebook +
    inf_shaq + inf_kylie + inf_mrbeast + inf_logan + inf_curry +
    inf_taylor + inf_ryan + inf_ksi + inf_charli +
    number_of_comments:number_of_likes +
    number_of_comments:writting_style +
    number_of_comments:influencer +
    number_of_likes:writting_style +
    number_of_likes:influencer +
    writting_style:influencer +
    number_of_comments:plt_instagram + number_of_comments:plt_tiktok +
    number_of_comments:plt_youtube + number_of_comments:plt_x +
    number_of_likes:plt_instagram + number_of_likes:plt_tiktok +
    number_of_likes:plt_youtube + number_of_likes:plt_x +
    writting_style:plt_instagram + writting_style:plt_tiktok +
    writting_style:plt_youtube + writting_style:plt_x +
    influencer:plt_instagram + influencer:plt_tiktok +
    influencer:plt_youtube + influencer:plt_x +
    number_of_comments:inf_kylie + number_of_comments:inf_mrbeast +
    number_of_comments:inf_logan + number_of_comments:inf_taylor +
    number_of_likes:inf_kylie + number_of_likes:inf_mrbeast +
    number_of_likes:inf_logan + number_of_likes:inf_taylor +
    writting_style:inf_kylie + writting_style:inf_mrbeast +
    writting_style:inf_logan + writting_style:inf_taylor +
    influencer:inf_kylie + influencer:inf_mrbeast +
    influencer:inf_logan + influencer:inf_taylor,
  data  = pdata,
  model = "random"
)
summary(model_auth_int)

## Report Findings Here:
##
##
```

------------------------------------------------------------------------

## Bayesian Hierarchical Models

Note: these models use `brms` and call Stan to compile — first run will take several minutes per model. Subsequent runs are faster. Random effects are nested: respondents (ResponseId) within scenarios.

```{r}
# Shared priors — weakly informative
priors <- c(
  prior(normal(0, 5),  class = "b"),        # fixed effects
  prior(normal(0, 10), class = "Intercept"),# intercept
  prior(cauchy(0, 2),  class = "sd")        # random effect SDs
)

# --- Purchase Intent ---
bayes_purchase <- brm(
  formula = purchase_intent ~
    number_of_comments + number_of_likes + writting_style + influencer +
    age_range + gender + income_level + education + race +
    employment_status + marritial_status +
    influencer_interaction + social_media_use + product_purchase +
    plt_instagram + plt_snapchat + plt_tiktok + plt_x +
    plt_youtube + plt_twitch + plt_facebook +
    inf_shaq + inf_kylie + inf_mrbeast + inf_logan + inf_curry +
    inf_taylor + inf_ryan + inf_ksi + inf_charli +
    (1 | ResponseId) + (1 | scenario),
  data   = cleaned_data,
  family = gaussian(),
  prior  = priors,
  chains = 4,
  iter   = 2000,
  warmup = 1000,
  cores  = parallel::detectCores(),
  seed   = 42
)
summary(bayes_purchase)
pp_check(bayes_purchase, ndraws = 100)  # posterior predictive check

## Report Findings Here:
##
##
```

```{r}
# --- Perceived Honesty ---
bayes_honesty <- brm(
  formula = percived_honesty ~
    number_of_comments + number_of_likes + writting_style + influencer +
    age_range + gender + income_level + education + race +
    employment_status + marritial_status +
    influencer_interaction + social_media_use + product_purchase +
    plt_instagram + plt_snapchat + plt_tiktok + plt_x +
    plt_youtube + plt_twitch + plt_facebook +
    inf_shaq + inf_kylie + inf_mrbeast + inf_logan + inf_curry +
    inf_taylor + inf_ryan + inf_ksi + inf_charli +
    (1 | ResponseId) + (1 | scenario),
  data   = cleaned_data,
  family = gaussian(),
  prior  = priors,
  chains = 4,
  iter   = 2000,
  warmup = 1000,
  cores  = parallel::detectCores(),
  seed   = 42
)
summary(bayes_honesty)
pp_check(bayes_honesty, ndraws = 100)

## Report Findings Here:
##
##
```

```{r}
# --- Perceived Authenticity ---
bayes_auth <- brm(
  formula = percived_authenticity ~
    number_of_comments + number_of_likes + writting_style + influencer +
    age_range + gender + income_level + education + race +
    employment_status + marritial_status +
    influencer_interaction + social_media_use + product_purchase +
    plt_instagram + plt_snapchat + plt_tiktok + plt_x +
    plt_youtube + plt_twitch + plt_facebook +
    inf_shaq + inf_kylie + inf_mrbeast + inf_logan + inf_curry +
    inf_taylor + inf_ryan + inf_ksi + inf_charli +
    (1 | ResponseId) + (1 | scenario),
  data   = cleaned_data,
  family = gaussian(),
  prior  = priors,
  chains = 4,
  iter   = 2000,
  warmup = 1000,
  cores  = parallel::detectCores(),
  seed   = 42
)
summary(bayes_auth)
pp_check(bayes_auth, ndraws = 100)

## Report Findings Here:
##
##
```

```{r}
# --- Model comparison via LOO-CV ---
loo_purchase <- loo(bayes_purchase)
loo_honesty  <- loo(bayes_honesty)
loo_auth     <- loo(bayes_auth)

print(loo_purchase)
print(loo_honesty)
print(loo_auth)
```

```{r}
# --- RMSE comparison across PLM, CV, and Bayesian models ---

# CV RMSE (already have these)
rmse_cv <- bind_rows(
  collect_metrics(cv_purchase) |> filter(.metric == "rmse") |>
    mutate(outcome = "purchase_intent", model = "10-fold CV (LM)"),
  collect_metrics(cv_honesty) |> filter(.metric == "rmse") |>
    mutate(outcome = "percived_honesty", model = "10-fold CV (LM)"),
  collect_metrics(cv_auth) |> filter(.metric == "rmse") |>
    mutate(outcome = "percived_authenticity", model = "10-fold CV (LM)")
) |> select(outcome, model, rmse = mean)

# Bayesian RMSE — posterior predictive RMSE
bayes_rmse <- function(fit, outcome_col) {
  obs  <- fit$data[[outcome_col]]
  pred <- fitted(fit)[, "Estimate"]
  sqrt(mean((obs - pred)^2))
}

rmse_bayes <- tibble(
  outcome = c("purchase_intent", "percived_honesty", "percived_authenticity"),
  model   = "Bayesian Hierarchical",
  rmse    = c(
    bayes_rmse(bayes_purchase, "purchase_intent"),
    bayes_rmse(bayes_honesty,  "percived_honesty"),
    bayes_rmse(bayes_auth,     "percived_authenticity")
  )
)

# PLM RMSE
plm_rmse <- function(mod) sqrt(mean(residuals(mod)^2))

rmse_plm <- tibble(
  outcome = c("purchase_intent", "percived_honesty", "percived_authenticity"),
  model   = "PLM Random Effects (base)",
  rmse    = c(
    plm_rmse(model_purchase),
    plm_rmse(model_honesty),
    plm_rmse(model_auth)
  )
)

rmse_plm_int <- tibble(
  outcome = c("purchase_intent", "percived_honesty", "percived_authenticity"),
  model   = "PLM Random Effects (interaction)",
  rmse    = c(
    plm_rmse(model_purchase_int),
    plm_rmse(model_honesty_int),
    plm_rmse(model_auth_int)
  )
)

# Combine and display
rmse_all <- bind_rows(rmse_cv, rmse_bayes, rmse_plm, rmse_plm_int) |>
  arrange(outcome, rmse)

print(rmse_all, n = Inf)
```
